\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{url}
\geometry{margin=1in}

\title{CSE 123A - Winter 2026}
\author{Group 8}
\date{}

\begin{document}
\pagestyle{fancy}
\maketitle

\fancyfoot{}
\fancyhead{}
\fancyfoot[R]{\thepage}

% Problem Statement
\section*{Problem statement}
Living with roommates can sometimes mean your filtered water device is empty when you need water. This can be very frustrating and leave you needing to drink tap water while other roommates get to drink cold refrigerated and filtered water. 

% Need Statement
\section*{Need Statement}
\textbf{We want a way to know if the container is out of water when we need water. }
\begin{itemize}
    \item Avoid having no water left in addition to everybody using the water filter, not knowing there is no water left.

    \item Need a way to know the current the water level of the pitcher so that it isn't empty without everyone knowing it's empty. 
    
    \item We need to know if the container is empty, in order to not run out of clean fresh water. 
\end{itemize}


% Goal
\section*{Goal}
\begin{itemize}
    \item Keeping water level known at all times, while informing to everybody in the household if the water level runs too low.
    \item Create a system to inform users if the container is empty. 
\end{itemize}
\textbf{If the container is empty, inform users.}

% Personas and Users
\section*{Personas and Users}
Intended for households 

% TimeLine
\section*{Timeline}

\end{document}
