\documentclass[12pt]{article}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{url}
\geometry{margin=1in}

\title{CSE 123A - Winter 2026}
\author{Group 8}
\date{}

\begin{document}
\pagestyle{fancy}
\maketitle

\fancyfoot{}
\fancyhead{}
\fancyfoot[R]{\thepage}

This first week was spent as a setup week. We spent our TA meeting discussing and working on our Need/Goal statements, and Personas. Our project is a water level device that can alert a group of users about the status of their shared container. 

\section*{Need/Goal}

We came to a conclusion regarding what our need for this device will be. We discussed various pieces at length and included some of our thoughts in our working document that's inside our Git repository. Our statements needed to align with each other as opposites. 

\section*{Personas}

Once we had a goal in mind we created three example users. The users were inspired by personal experience and need for this type of device. The example users cover a wide range of characteristics, which we feel represent the intended user base. 

\section*{Contribution Tools}

During our meeting, we began setting up the infrastructure to work on the project, including our tools and repositories that will be used to track and combine contributions. We discussed various tools and integrations and decided on using GitLab for the main project repository, as well as Overleaf to work on the \LaTeX\ documentation files. 

\section*{Short Term Future Goals}

Over the next week, we plan on finalizing the tools needed to work together and verifying that the contribution metrics are being tracked. We are also working on finishing up the character profiles to reflect some different classes of possible users.


\end{document}
